Plant Modeling for an Autonomous Vehicle

### 2022-04-20 poster.tex

%-----------------------------------------------------------
% PROBLEM SETUP
%-----------------------------------------------------------
%\vskip -1cm
\begin{alertblock}{Problem Setup}
%\vskip -1cm
%\begin{enumerate}
%    \item Develop and linearize system model
%    \item Simulate algorithms in MATLAB
%    \item Test algorithms on desktop computer using USB connection 
%    \item Test algorithms on Raspberry Pi microcontroller
%    \item Test algorithms on mobile device
%\end{enumerate}

%\vskip -1cm
$\bullet$ Conducted a literature review to look for existing solutions
$\bullet$ System Architecture 
\begin{figure}
	\centering
	\begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=0.75 cm]
    \tikzstyle{sum} = [draw, circle,fill=orange!15]
    % place nodes
    \node[sum](sum){$\sum$};
    \node[block,right of=sum,node distance=2 cm, text width=1.25cm,text centered](steeringController){Steering controller};
    \node[block,right of=steeringController,node distance=2.25 cm, text width=1.3cm,text centered](steeringSubsystem){Steering subsystem};

    % Connections
    \draw[stealth-,thick]
    (sum.west)--node[very near start,above]{$+$}++(-0.5,0)node[above]{$\theta^{\text{ref}}$};
    \draw[-stealth,thick]
    (sum.east)--node[midway,above]{Error}(steeringController);
    \draw[-stealth,thick]
    (steeringController.15)--node[midway,above]{$v_A$}(steeringSubsystem.165);
    \draw[-stealth,thick]
    (steeringController.-15)--node[midway,above]{$v_B$}(steeringSubsystem.-165);
    \draw[-stealth,thick]
    (steeringSubsystem.east) --coordinate (tt) ++(0.5,0)node[above]{$\theta(t)$};
    \fill
    ($(steeringSubsystem.east)+(0.25,0)$) circle [radius=2pt];
    \draw[-stealth,thick]
    (tt) -- ++(0,-0.75) -|(sum.south)node[pos=0.9,left]{$-$};

  \end{tikzpicture}
  % \captionsetup{justification=centering, margin=3cm}

  % \includegraphics[width=2.5in]{figs/inkscape/steeringModelBlockDiagram}
  \caption{Steering subsystem block diagram.}
  \label{fig:steeringModelBlockDiagram}
\end{figure}

\begin{figure}
	\centering
	 \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width= 5 cm, minimum height=1.5 cm]
    % place nodes
    \node[block,text width=1.75cm,text centered](accelSubsystem){Acceleration subsystem};
    % Connections
    \draw[stealth-,thick]
    (accelSubsystem.180)--node[very near end,above]{Acceleration pedal voltages}++(-5.0,0);
    \draw[-stealth,thick]
    (accelSubsystem.0)--node[very near end,above]{Acceleration pedal position}++(5.0,0);
  \end{tikzpicture}
    \caption{Acceleration subsystem block diagram}
    \label{fig:accelModelArchitecture}
\end{figure}

\begin{figure}
	\centering
	  \begin{tikzpicture}
    \tikzstyle{every node} = [font=\footnotesize]
    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2.0 cm]
    % place nodes
    \node[block,text width=1.25cm,text centered](brakeSubsystem){Brake subsystem};

    % Connections
    \draw[stealth-,thick]
    (brakeSubsystem.140)--node[pos=0.65,above]{Pressure voltages}++(-4.5,0);
    \draw[stealth-,thick]
    (brakeSubsystem.180)--node[pos=0.65,above]{Stroke voltages}++(-4.5,0);
    \draw[stealth-,thick]
    (brakeSubsystem.-140)--node[pos=0.65,above]{On/Off switch}++(-4.5,0);
    \draw[-stealth,thick]
    (brakeSubsystem.30)--node[pos=0.5,above]{Pedal position}++(4.5,0);
    \draw[-stealth,thick]
    (brakeSubsystem.-30)--node[pos=0.5,below]{Brake pressed}++(4.5,0);

  \end{tikzpicture}
    % \captionsetup{justification=centering, margin=3cm}
    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
    \caption{Brake subsystem block diagram}
    \label{fig:brakeModelArchitecture}
\end{figure}

%\begin{figure}
%    \centering
%        \begin{tikzpicture}
%    \tikzstyle{every node} = [font=\footnotesize]
%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
%    % place nodes
%    \node[block,text width=1.75cm,text centered](speedControlSubsystem){Speed Control subsystem};
%
%    % Connections
%    \draw[stealth-,thick]
%    (speedControlSubsystem.180)--node[very near end,above]{Desired vehicle speed}++(-4.0,0);
%    \draw[-stealth,thick]
%    (speedControlSubsystem.0)--node[very near end,above]{Actual vehicle speed}++(4.0,0);
%    
%  \end{tikzpicture}
%    \caption{Speed Control subsystem block diagram}
%    \label{fig:speedControlModelArchitecture}
%
%\end{figure}
%
%
%\begin{figure}
%    \centering
%  \begin{tikzpicture}
%    \tikzstyle{every node} = [font=\footnotesize]
%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=2 cm]
%    % place nodes
%    \node[block,text width=1.25cm,text centered](speedSubsystem){Speed subsystem};
%
%    % Connections
%    \draw[stealth-,thick]
%    (speedSubsystem.140)--node[very near end,above]{Acceleration pedal position}++(-5.0,0);
%    \draw[stealth-,thick]
%    (speedSubsystem.180)--node[very near end,above]{Brake pedal position}++(-5.0,0);
%    \draw[stealth-,thick]
%    (speedSubsystem.-140)--node[near end,above]{Shifter Gear}++(-5.0,0);
%    \draw[-stealth,thick]
%    (speedSubsystem.0)--node[near end,above]{Vehicle Speed}++(5.0,0);
%    
%  \end{tikzpicture}
%    % \captionsetup{justification=centering, margin=3cm}
%    % \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
%    \caption{ Speed subsystem block diagram}
%    \label{fig:speedModelArchitecture}
%\end{figure}

%\begin{figure}
%    \centering
%\begin{tikzpicture}
%    \tikzstyle{every node} = [font=\footnotesize]
%    \tikzstyle{block} = [draw, rectangle, fill=green!15, rounded corners=5pt, minimum width=4.5 cm, minimum height=1.5 cm]
%    % place nodes
%    \node[block,text width=1.75cm,text centered](shiftSubsystem){Shift subsystem};
%
%    % Connections
%    \draw[stealth-,thick]
%    (shiftSubsystem.180)--node[very near end,above]{Desired Shifter Gear}++(-4.5,0);
%    \draw[-stealth,thick]
%    (shiftSubsystem.0)--node[very near end,above]{Actual Shifter Gear}++(4.5,0);
%    
%  \end{tikzpicture}
%    \caption{Shift subsystem block diagram}
%    \label{fig:shiftModelArchitecture}
%\end{figure}

@@

\begin{figure}
    \centering
		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
	\caption{Steering System Training Plots}
    \label{fig:SteeringSysNeuralNetwork}
\end{figure}

\begin{figure}
    \centering
		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}
	\caption{Acceleration System Training Plots}
    \label{fig:AccelerationSysNeuralNetwork}
\end{figure}

\begin{figure}
    \centering
		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFig}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
	\caption{Brake System Training Plots}
    \label{fig:BrakeSysNeuralNetwork}
\end{figure}

@@

\begin{enumerate}
	\item Approximate neural network signal
	\begin{align*}
  		\hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
  	\end{align*}
  	\item Define the weight matrix
  	\begin{align*}
  		{\bf W}_a = 
  		\begin{bmatrix}
    		w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
    		w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
    		\vdots & \ddots & \ldots &\vdots\\
    		w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
  		\end{bmatrix}.
	\end{align*}
	\item Compute the sum-of-squared error
	\begin{align*}
    		\bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
    		% \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
  	\end{align*}	
  	\begin{align*}
  		\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}}
  	\end{align*}
	\begin{align*}
    		\delta_a = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
  	\end{align*}
  	\item Find the actor weight by minimizing the sum-of-square error
  	\begin{align*}
  	\delta_a = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
	\end{align*}
	\item Take the derivative of $\delta_a$ with respect to ${\bf W}_a$ and set $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero
	\begin{align*}
  		\frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T 					\bm{\Sigma}\mathbf{W}_a
	\end{align*}
	\begin{align*}
  		{\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
	\end{align*}
	\item Use the gradient descent approach to minimize the least square order alter weights when training the neural network
	\begin{multline*}
  		\mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}\\
  		=\mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}				_a^{(r)}\right)\\
  		= \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
	\end{multline*}
\end{enumerate}

>>>>

%-----------------------------------------------------------
% PROBLEM SETUP
%-----------------------------------------------------------
%\vskip -1cm
\begin{alertblock}{Problem Setup}

%\vskip -1cm
\begin{itemize}
	\item Conducted a literature review to look for existing solutions
	\item System Architecture 
\end{itemize}

\begin{figure}
	\centering
	\includegraphics[width=1.0\linewidth]{figs/inkscape/steeringModelBlockDiagram}
	\caption{Steering subsystem block diagram}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.48\linewidth]{figs/inkscape/accelerationModelArchitecture}
	\caption{Acceleration subsystem block diagram}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.48\linewidth]{figs/inkscape/brakeModelArchitecture}
	\caption{Brake subsystem block diagram}
\end{figure}

@@

\begin{figure}
    \centering
		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
		{\includegraphics[width=0.48\linewidth]{figs/img/steeringNeuralNetworkTrainedOutput}}
	\caption{ Steering System Training Plots}
    \label{fig:SteeringSysNeuralNetwork}
\end{figure}

%\begin{figure}
%    \centering
%		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput}}
%		{\includegraphics[width=0.48\linewidth]{figs/img/accelNeuralNetworkTrainedOutput2}}
%	\caption{Acceleration System Training Plots}
%    \label{fig:AccelerationSysNeuralNetwork}
%\end{figure}

\begin{figure}
    \centering
		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFig}}
		{\includegraphics[width=0.48\linewidth]{figs/img/brake_new_neuralNetworkFigLog2Test}}
	\caption{ Brake System Training Plots}
    \label{fig:BrakeSysNeuralNetwork}
\end{figure}

@@

%\begin{enumerate}
%	\item Approximate neural network signal
%	\begin{align*}
%  		\hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
%  	\end{align*}
%  	\item Define the weight matrix
%  	\begin{align*}
%  		{\bf W}_a = 
%  		\begin{bmatrix}
%    		w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
%    		w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
%    		\vdots & \ddots & \ldots &\vdots\\
%    		w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
%  		\end{bmatrix}.
%	\end{align*}
%	\item Compute the sum-of-squared error
%	\begin{align*}
%    		\bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
%    		% \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
%  	\end{align*}	
%  	\begin{align*}
%  		\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}}
%  	\end{align*}
%	\begin{align*}
%    		\delta_a = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
%  	\end{align*}
%  	\item Find the actor weight by minimizing the sum-of-square error
%  	\begin{align*}
%  	\delta_a = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
%	\end{align*}
%	\item Take the derivative of $\delta_a$ with respect to ${\bf W}_a$ and set $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero
%	\begin{align*}
%  		\frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T 					\bm{\Sigma}\mathbf{W}_a
%	\end{align*}
%	\begin{align*}
%  		{\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
%	\end{align*}
%	\item Use the gradient descent approach to minimize the least square order alter weights when training the neural network
%	\begin{multline*}
%  		\mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}\\
%  		=\mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}				_a^{(r)}\right)\\
%  		= \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
%	\end{multline*}
%\end{enumerate}

\begin{figure}
    \centering
		\includegraphics[width=0.80\linewidth]{figs/img/steeringSimulinkBlock}
	\caption{Steering Neural Network Simulink Model}
    \label{fig:steeringNeuralNetwork}
\end{figure}

\begin{figure}
    \centering
		\includegraphics[width=0.80\linewidth]{figs/img/accelerationSimulinkBlock}
	\caption{Acceleration Neural Network Simulink Model}
    \label{fig:accelNeuralNetwork}
\end{figure}

\begin{figure}
    \centering
		\includegraphics[width=0.80\linewidth]{figs/img/brakeSimulinkBlock}
	\caption{Brake Neural Network Simulink Model}
    \label{fig:brakeNeuralNetwork}
\end{figure}
